EDA

### 2024-11-28 other/EDA/EDA.qmd
fixed file structure

df <- df %>% select(-link)

@@

```{r}
hist(df$amount,
     breaks = 30,  # Number of bins; adjust as needed
     main = "Distribution of Award Amounts",
     xlab = "Award Amount (CAD)",
     ylab = "Frequency",
     col = "skyblue",
     border = "black")

>>>>

View(df)

@@

```{r}
#View(df)

# Define the bin width
bin_width <- 100000

# Determine the range of 'amount'
min_amount <- floor(min(df$amount, na.rm = TRUE) / bin_width) * bin_width
max_amount <- ceiling(1000000000 / bin_width) * bin_width

# Create a sequence of breaks
breaks <- seq(min_amount, max_amount, by = bin_width)

# Categorize 'amount' into bins
df$amount_bin <- cut(df$amount, breaks = breaks, right = FALSE, include.lowest = TRUE)

# Count the number of contracts in each bin
contract_counts <- table(df$amount_bin)

# Convert to a dataframe for better readability
contract_counts_df <- as.data.frame(contract_counts)
colnames(contract_counts_df) <- c("Amount_Range", "Contract_Count")

# View the counts
print(contract_counts_df)

# Basic Bar Plot
barplot(contract_counts,
        main = "Number of Contracts per 1,000,000 CAD Bin",
        xlab = "Award Amount (CAD)",
        ylab = "Number of Contracts",
        col = "skyblue",
        las = 2,  # Make label text perpendicular to axis
        cex.names = 0.7)  # Adjust label size if needed
